Jeff Goldsmith

### 2017-08-09 teaching.Rmd
placeholder for link to DSI course
links to DSI and ICAMPAM shortcourse

Fall 2017: Data Science I

@@

2017: ["Variable Selection Methods in Functional Regression"](http://jeffgoldsmith.com/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)

>>>>

Fall 2017: [Data Science I](http://jeffgoldsmith.com/DSI/)

@@

2017: ["Functional Data Analysis for Wearables: Methods and Applications"](http://jeffgoldsmith.com/ICAMPAM/) (at the International Conference on Ambulatory Monitoring of Physical Activity)  
2017: ["Variable Selection Methods in Functional Regression"](http://jeffgoldsmith.com/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)
